---
title: "Weight of Fish"
author: "Skye Solis"
date: "Summer 2024"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
require(leaps)
```

# Predicting Fish Weight

```{r}
Fish <- Fish %>%

mutate(across(where(is.character), as.factor))

levels(Fish$Species)
```

```{r}
fish <- read.csv(file = "Fish.csv)
```

```{r}
Bream <- filter(Fish, Species == 

"Bream")

Bream <- select(Bream, -Species) 

Parkki <- filter(Fish, Species == 

"Parkki")

Parkki <- select(Parkki, -Species) 

Perch <- filter(Fish, Species == 

"Perch")

Perch <- select(Perch, -Species) 

Pike <- filter(Fish, Species == 

"Pike")

Pike <- select(Pike, -Species) 

Roach <- filter(Fish, Species == 

"Roach")

Roach <- select(Roach, -Species) 

Smelt <- filter(Fish, Species == 

"Smelt")

Smelt <- select(Smelt, -Species) 

Whitefish <- filter(Fish, Species == 

"Whitefish")

Whitefish <- select(Whitefish, -Species)



## Perch

### Best Models

### Best Two regressor model


## Pike

### Best Models

### Best Two regressor model

## Roach

### Best Models

### Best Two regressor model

## Final Summary Statements
```


```{r}
regsubsets.out <-

    regsubsets(Weight ~ .,

               data = Perch,

               nbest = 

1,       

# 1 best model for each number of predictors

               nvmax = 

NULL,    

# NULL for no limit on number of variables

               force.in = 

NULL, force.out = 

NULL,

               method = 

"exhaustive")

summary.out <- summary(regsubsets.out)

as.data.frame(summary.out$outmat)
```


```{r}

library(leaps)

regsubsets.out <-

    regsubsets(Weight ~ .,

               data = Perch,

               nbest = 1,       # 1 best model for each number of predictors

               nvmax = NULL,    # NULL for no limit on number of variables

               force.in = NULL, force.out = NULL,

               method = "exhaustive")

 

summary.out <- summary(regsubsets.out)

as.data.frame(summary.out$outmat)

library(car)

subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")

```

```{r}
Perchmodel <- lm(Weight~Height+Width, data=Perch)
summary.lm(Perchmodel)
```


The best model based on this growth is the Perch model.


The best models are the two element models of height and width. 

to find out the comparative data between, Perch, Pike and Roach, we used the leap program to tind out the best regressor models.
Using leaps we can display all the appropriate data, such as the Adjusted R squared number to find out which model when compared to the variable weight had an impact on the outcome.
In this case we took note of the Adjusted R sgaured number and the best two regressor models in each fish species.

